Items

### 2024-04-12 manuscript.Rmd
reknitted manuscript removed unnecessary files
- rerendered ms

note: |
  This paper is in-principle-accepted at as a Stage 1 Registered Report at Collabra.

@@

documentclass     : "apa6"
# classoption       : "man"
# output: html_document
output            : papaja::apa6_pdf
# output            : papaja::apa6_word

>>>>

# note: |
  # This paper is in-principle-accepted at as a Stage 1 Registered Report at Collabra.

@@

documentclass     : "apa6"
# classoption       : "man"
# output            : html_document
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
